---
title: "Basic EDA of Data"
output: github_document
---
<br><h3>Installing Data</h3><br>
Install "coinmarketcapr" data package.
```{r}
library(coinmarketcapr)
library(ggplot2)
library(dplyr)
key <- '948b8972-8b87-4632-975a-1f557e76cfe2'
coinmarketcapr::setup(key)

```


<br><h3>Market Cap</h3><br>
The following function plots the top 15 currencies with the largest marketcaps, this shows us which coins are safer investments as large cap coins are considered more conservative.
```{r}
cryptos <- get_crypto_listings()
market_cap <- cryptos$USD_market_cap
names <- cryptos$name
crypto_table <- data.frame(names,market_cap)
ordered <- order(crypto_table)
crypto_ordered <- crypto_table[,-9]
crypto_ordered
barplot(crypto_ordered$market_cap[1:15], col=rainbow(20), names.arg= crypto_ordered$names[1:15],las=2)

```

<br><h3>Percent Change 30 days</h3><br>
We can further create charts showing which coins have had a large positive percent change in the past 30 days.

```{r}
cryptos <- get_crypto_listings()
thirtydpercent <- cryptos$USD_percent_change_30d
names <- cryptos$name
cryptothirtyd <- data.frame(names,thirtydpercent)
thirtydordered <- cryptothirtyd[order(cryptothirtyd$thirtydpercent, decreasing = TRUE), ]
thirtydordered

barplot(thirtydordered$thirtydpercent[1:15], col=rainbow(20), names.arg= thirtydordered$names[1:15],las=2)
```


<br><h3>Percent Change 7 days</h3><br>
We can do something similar with the following and see which coins have had a significant percent change in the past 7 days.

```{r}
cryptos <- get_crypto_listings()
sevendpercent <- cryptos$USD_percent_change_7d
names <- cryptos$name
cryptosevend <- data.frame(names,sevendpercent)
sevendordered <- cryptosevend[order(cryptosevend$sevendpercent, decreasing = TRUE), ]
sevendordered

barplot(sevendordered$sevendpercent[1:15], col=rainbow(20), names.arg= sevendordered$names[1:15],las=2)
```


<br><h3>Percent Change 24h</h3><br>
Further we can do the same thing on a smaller scale to see which currencies have changed the most in the past 24 hours.

```{r}
cryptos <- get_crypto_listings()
twentyfourpercent <- cryptos$USD_percent_change_24h
names <- cryptos$name
cryptotwentyfour <- data.frame(names,twentyfourpercent)
twentyfourordered <- cryptotwentyfour[order(cryptotwentyfour$twentyfourpercent, decreasing = TRUE), ]
twentyfourordered

barplot(twentyfourordered$twentyfourpercent[1:15], col=rainbow(20), names.arg= twentyfourordered$names[1:15],las=2)
```

<br><h3>Percent Change 24h</h3><br>
We can also chart the volume of the currency in order to see how much of the financial asset has been traded in the past day. Seeing a high volume shows us that a stock has high security as it is more liquid and is more actively trading.

```{r}
cryptos <- get_crypto_listings()
volume <- cryptos$USD_volume_24h
names <- cryptos$name
cryptovolume <- data.frame(names,volume)
volumeordered <- cryptovolume[order(cryptovolume$volume, decreasing = TRUE), ]
volumeordered

barplot(volumeordered$volume[1:15], col=rainbow(20), names.arg= volumeordered$names[1:15],las=2)
```

```{r}
#libraries
library(deSolve)
library(shiny)
library(shinyWidgets)
library(cryptor)
library(ggplot2)
library(plotly)

#Setting up data
btc_price_history_full = get_historical_price("BTC", "USD", limit = 2000)
btc_price = btc_price_history_full$close
btc_time = as.Date(btc_price_history_full$time)
btc_frame = data.frame(btc_time, btc_price)

#Plotting data
btc_plot <- ggplot(btc_frame, aes(x = btc_time, y=btc_price)) +
  geom_line() + 
  xlab("Time") +
  ylab("Bitcoin Price")

btc_plot <- ggplotly(btc_plot)
btc_plot

```
<br><h3>By: Aaditya Surya</h3><br>